---
date: "`r paste0('Report Date: ', Sys.Date())`"
output: 
  officedown::rdocx_document:
    reference_docx: template_officedown.docx
---

```{r setup, include=FALSE}
options(knitr.duplicate.label = 'allow')
options(tinytex.verbose = TRUE)

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      error = TRUE,
                      cache = FALSE,
                      cache.comments = FALSE,
                      include = TRUE,
                      autodep = TRUE,
                      eval = TRUE)

library(readxl)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(plotly)
library(scales)
library(zoo)
library(knitr)

load("report_region.RData")

```

*Cut to the email recipient field:*

**TO:**

`r if(unique(bc_region$REGION)=="Eastern Region"){email.address_ER}`
`r if(unique(bc_region$REGION)=="Northwest Region"){email.address_NWR}`
`r if(unique(bc_region$REGION)=="Western Region"){email.address_WR}`

**CC:**

`r email.address_cc`

*Cut to the email contents:*

Hello all,

Below is the statewide update for satellite imagery of cyanobacteria in `r unique(bc_region$REGION)` waterbodies.

Please note in the report that:

*   The 7-Day Average Daily Maximum is now used for summarizing the cyanobacterial cell counts.       

*   The table includes all waterbodies with 7-Day Average Daily Maximum of cell counts above WHO thresholds (100,000 cells/mL) in the last 7 days.        

*   The time series plots include all resolvable waterbodies identified from EPA’s CyAN project. The plots report both the daily average and daily maximum cell counts from April 1st through the present.       

*	All data presented in this report are provisional and subject to change. We suggest examining additional imagery from Sentinel 2 (https://www.sentinel-hub.com/explore/sentinelplayground/) or following up with site visits if necessary.    

Cheers!

*DELETE ABOVE AFTER CUT AND PASTE*

---
title: "`r paste0("CyAN Update (2021-04-01 - ", max(dta2$Date), ") for ",r)`"
---

Attn: `r knitr::combine_words(unique(sort(bc_region$STAFF)))`

---------------------------------------------------------------------------------------------------------------------

<!---BLOCK_LANDSCAPE_START--->

```{r table, echo=FALSE, results = 'asis'}

if(num>10){
  
  knitr::kable(tbl.7dmdm[1:num,], caption = caption_2)
  
} else {
  
  numb <- nrow(tbl.7dmdm[which(!tbl.7dmdm$`7-Day Average Daily Maximum (cells/mL)` == "Non-detect"),])
  
  if(num == numb){
    
    knitr::kable(tbl.7dmdm[1:num,], caption = caption_2)
    
  } else {
    
    knitr::kable(tbl.7dmdm[1:numb,], caption = caption_3)
  }
  
}
```

---------------------------------------------------------------------------------------------------------------------

`r paste0("Figures: Time series plots of daily maximums and daily means of cyanobacteria abundance (cells/mL) of the waterbodies during 2021-04-01 and ", as.Date(max(dta2$Date)), " in the ", r, ".")`

```{r ggplot, fig.width=10, fig.height=5, echo=FALSE}

for(i in gnisidname) {
  
  dta.plot <- dta %>% dplyr::filter(as.Date(Date) >= as.Date("2021-04-01"))
  
  plot <- ggplot(subset(dta.plot, dta.plot$GNISIDNAME == i),
                 aes(x=as.Date(Date), 
                     y=`Cyanobacteria (cells/mL)`,
                     group=`Summary Statistics`,
                     color=`Summary Statistics`)) +
    geom_line(size=1.5) +
    geom_point(color="black", alpha=0.3, size=3) +
    xlab("Date") +
    scale_x_date(date_labels = "%b-%d",
                 date_breaks = "week") +
    ylab("Cyanobacteria (cells/mL)") +
    #scale_y_continuous(labels = comma) +
    scale_y_continuous(trans = log10_trans(),
                       breaks = trans_breaks("log10", function(x) 10^x),
                       labels = trans_format("log10", math_format(10^.x))) +
    geom_hline(yintercept=100000,linetype="dashed",color="red",size=1.5) +
    annotate("text", as.Date(min(dta.plot$Date)), 100000, vjust = 1, hjust = 0,  label = "WHO Guideline") +
    ggtitle(i) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 10),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12),
          plot.title = element_text(size=15))
  
  print(plot)
  
}

```

<!---BLOCK_LANDSCAPE_STOP--->